An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-06-17 Manuscript revise 20190612.tex
333

For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{red}have been developed recently. However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver, but the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used. All these makes easily deduce the relation across a non-linear wave. Although there are many  cases considered in their works \cite{gao20171d,gao2018complete}, for every case, they can easily obtain the exact solution. But for many engineering problems, the EOS is more complex, and the energy equation has to be included during simulating. For these engineering solid problems with a complex constitutive and a complex EOS, such as the Mie-Gr\"uneisen EOS, up to now, there is no  exact Riemann solution.

@@

In this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition. As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely  in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave. Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves. These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves. Moreover, elastic wave runs always faster than the followed plastic wave. So there are thirty-six possible cases of the wave structures in the Riemann solver.
%For a given case, we will obtain theoretical relations of all the states as functions of density. At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained. Also, the half Riemann problem and its exact solution are considered in this paper.

@@

The derivatives of $f_{u(k)}$ and $f_{\sigma(k)}$ are given as
\begin{equation}
  \frac{\partial f_{u(k)}}{\partial \rho^*_{L(R)}} = \frac{f_{u(k)}-f_{u(k-1)}}{\rho_{L(R)(k)}^* - \rho_{L(R)(k-1)}},\quad
  \frac{\partial f_{\sigma(k)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma(k)}-f_{\sigma(k-1)}}{\rho_{L(R)(k)}^* - \rho_{L(R)(k-1)}}.
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{u(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
  \frac{\partial f_{u(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
\end{equation}
where $\Delta \rho$ is a little quantity, we define
\begin{equation}
  \Delta \rho = \frac{\rho_{L(R)(1)}^*}{100}.
\end{equation}

@@

{\color{red}
\begin{equation} \label{yield1}
  \left\{
  \begin{aligned}
	& \text{an elastic  rarefaction} & \text{if}  \ \hat{s}_{xxL(R)}<\frac{2}{3}Y^{0},\\
	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y_{0},\\
	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0},\\
	& \text{an elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0}.
\end{aligned}\right.
\end{equation}
}

@@

\textbf{Remark}:  In (\ref{rerpp}) and (\ref{rerpu}), there are two integral terms. Obviously, because of the complexity of the EOS, we can not get the exact integral values. We have to use the numerical methods to approximate the two integral terms with high order of accuracy. The approximation methods are introduced in the Appendix 1.

@@

	The initial density is  given as
\begin{equation}
\rho_{(0)}^* = \rho_R.
\end{equation}
\textbf{Iteration begin:}
\begin{enumerate}[Step 1]
  \item Case select:
	By a given  $\rho _{(k)}^*$ in $k$ iteration step, we need to determine the case of the wave structures in the left side. The determining  process is  also done in Section \ref{sec:deter}.

  \item Solving $f$:  After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.

  \item  Updating   $\rho^*$:   By the Newton iteration equation, a new density can be updated as

\begin{equation}
 \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
\end{equation}
The derivatives of $f$ is  given by
\begin{equation}
  \frac{\partial f_{(k+1)}}{\partial \rho^*} = \frac{f_{(k+1)}-f_{(k)}}{\rho_{(k+1)}^* - \rho^*_{(k)}},
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{(1)}}{\partial \rho^*} = \frac{f(\rho^*+\Delta \rho)-f(\rho^*)}{\Delta \rho},
\end{equation}
where $\Delta \rho$ is a little quatity, we can choose it as
\begin{equation}
  \Delta \rho = \frac{\rho_{(0)}^*}{100}.
\end{equation}
\item Convergence test:
The  convergence is meassured by
\begin{equation}
\text{CHA} = \text{max} \left[
\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right].
\end{equation}
and the tolerance is taken as $\text{TOL} = 10^{-4}$.

If $ \text{CHA} \le \text{TOL} $, the iteration ends.
It usually takes 2-4 step to get a convergence result.
\end{enumerate}
\textbf{Iteration end.}
\section{Numerical  tests }
In this section, by choosing suitable initial conditions, we will solve the Riemann problem with several different structure cases in the solution. For simple  expression, in figures, we use same representations as those in \cite{gao2018complete}. ``$|$'' means the contact wave, and capital letters ''S'' and ''R'' means the shock and rarefaction wave. Superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave.  Numerical results by the method  in \cite{liumulti} is used to verified the correctness of the exact solution. In the following tests, the materials are taken as  aluminium and copper. The parameters for the EOS and constitutive model for aluminum and copper  are
$ (\rho_0, a_0, \Gamma_0, s, \mu)_{\text{Al}} =(8930 \text{kg}/\text{m}^3, 3940 \text{m}/\text{s},2, 1.49, 2.76 ,2.76\times 10^{10} \text{Pa} )$ and   $(\rho_0, a_0, \Gamma_0, s, \mu)_{\text{copper}} =(2785 \text{kg}/\text{m}^3, 5328 \text{m}/\text{s},2, 1.338,4.5\times 10^{10}\text{Pa})$, respectively. The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.

@@

  %\includegraphics[width= 8cm] {case1rho.pdf}
  %\includegraphics[width= 8cm] {case1u.pdf}
  %\includegraphics[width= 8cm] {case1p.pdf}
  %\includegraphics[width= 8cm] {case1sigma.pdf}

    \caption{Comparison resutls for Test 1 with the structrures of $S^P|S^P$.  }
  \label{fig:case1}
\end{figure}
\subsection{Test 2}
Next, we consider a case with yielding process at both sides, so the result has five waves. The initial condition is
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 800\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, besides the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
\begin{figure}
  \centering
  %\includegraphics[width= 8cm] {case2rho.pdf}
  %\includegraphics[width= 8cm] {case2u.pdf}
  %\includegraphics[width= 8cm] {case2p.pdf}
  %\includegraphics[width= 8cm] {case2sxx.pdf}
  \caption{Comparison resutls for Test 1 with the structrures of $S^ES^P|S^PS^E$.  }
  \label{fig:case2}
\end{figure}

@@

 % \includegraphics[width= 8cm] {case4rho.pdf}
 % \includegraphics[width= 8cm] {case4u.pdf}
 % \includegraphics[width= 8cm] {case4p.pdf}
 % \includegraphics[width= 8cm] {case4sxx.pdf}

@@

%  \includegraphics[width= 8cm] {case3rho.pdf}
%  \includegraphics[width= 8cm] {case3u.pdf}
%  \includegraphics[width= 8cm] {case3p.pdf}
%  \includegraphics[width= 8cm] {case3sxx.pdf}

    \caption{Comparison resutls for Test 4 with the structrures of $R^ER^P|R^PR^E$.  }
  \label{fig:case4}
\end{figure}
\subsection{Test 5}
All the above four tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
&	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 1.0\times 10^8\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -40\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
In the Fig.\ref{fig:case5} shown in both the numerical and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.

@@

 % \includegraphics[width= 8cm] {case5rho.pdf}
 % \includegraphics[width= 8cm] {case5u.pdf}
 % \includegraphics[width= 8cm] {case5p.pdf}
 % \includegraphics[width= 8cm] {case5sxx.pdf}

    \caption{Comparison resutls for Test 5 with the structrures of $R^P|R^PR^E$.  }
  \label{fig:case5}
\end{figure}
\subsection{Test 6}
In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves producted into the higher pressure side and shock waves generated into the lower pressure side. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10} \text{Pa}, \quad s_{xx}= 0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side.
\begin{figure}
  \centering

 % \includegraphics[width= 8cm] {case9rho.pdf}
 % \includegraphics[width= 8cm] {case9u.pdf}
 % \includegraphics[width= 8cm] {case9p.pdf}
 % \includegraphics[width= 8cm] {case9sxx.pdf}

    \caption{Comparison resutls for Test 6 with the structrures of $R^ER^P|S^PS^E$.  }
  \label{fig:case9}
\end{figure}
\subsection{Test 7}
Now we will consider two multi-material tests with different materials on different sides. In this test, on the left side, a lighter material of aluminum with a velocity impacts to a heavier material of copper. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa},\\
	 &	 \text{R: Copper,}\quad  \rho = 8930\text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p =0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Show in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface. The exact Riemann solver can solve the Riemann problem with multi-materials very well comparing to the MHLLCEP approximate solver.

\begin{figure}
  \centering
 % \includegraphics[width= 8cm] {case6rho.pdf}
 % \includegraphics[width= 8cm] {case6u.pdf}
 % \includegraphics[width= 8cm] {case6p.pdf}
 % \includegraphics[width= 8cm] {case6sigma.pdf}

    \caption{Comparison results for Test 7 with structrures of $R^ER^P|R^PR^E$.  }
  \label{fig:case7}
\end{figure}

>>>>

For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{red}have been developed recently. However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver. But there are three shotcomings in their works. {\color{red}Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.  Secondly, the states of elastic and plastic is using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave. Thirdly, only the changing from  elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}

@@

In this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition. As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely  in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave. Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves. These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves. Moreover, elastic wave runs always faster than the followed plastic wave. So there are thirty-six possible cases of the wave structures in the Riemann solver. {\color{red} Both the  changing from elastic to plastic and  the converse changing from plastic to elastic are considered.}
%For a given case, we will obtain theoretical relations of all the states as functions of density. At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained. Also, the half Riemann problem and its exact solution are considered in this paper.

@@

The derivatives of $f_{u(k)}$ and $f_{\sigma(k)}$ are given as
\begin{equation}
  \frac{\partial f_{u(k)}}{\partial \rho^*_{L(R)}} = \frac{f_{u(k)}-f_{u(k-1)}}{\rho_{L(R)(k)}^* - \rho_{L(R)(k-1)}},\quad
  \frac{\partial f_{\sigma(k)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma(k)}-f_{\sigma(k-1)}}{\rho_{L(R)(k)}^* - \rho_{L(R)(k-1)}}.
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{u(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
  \frac{\partial f_{u(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
\end{equation}
where $\Delta \rho$ is a small quantity, we define
\begin{equation}
  \Delta \rho = \frac{\rho_{L(R)(1)}^*}{100}.
\end{equation}

@@

{\color{red}
\begin{equation} \label{yield1}
  \left\{
  \begin{aligned}
	& \text{an elastic  rarefaction} & \text{if}  \ \hat{s}_{xxL(R)}<\frac{2}{3}Y^{0},\\
	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y_{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y_{0},\\
	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y_{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0},\\
	& \text{an elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y_{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0}.
\end{aligned}\right.
\end{equation}
}

@@

\textbf{Remark}:  In (\ref{rerpp}) and (\ref{rerpu}), there are two integral terms. Obviously, because of the complexity of the EOS, we can not get the exact integral values. We have to use the numerical methods to approximate the two integral terms with high order of accuracy. The approximation methods are introduced in the Appendix A.

@@

	The initial density is  given as
\begin{equation}
\rho_{(1)}^* = \rho_R.
\end{equation}
\textbf{Iteration begin:}
\begin{enumerate}[Step 1]
  \item Determining the case of the wave structure:
	By a given  $\rho _{(k)}^*$ in the $k$-th iteration step, we can use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem. In this procedure for solving this Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.

  \item Solving $f(\rho^*,\mathbf{Q}_R)$:

	After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.

  \item Evaluating the derivative of  $f(\rho^*,\mathbf{Q}_R)$:

The derivatives of $f$ is  given by
\begin{equation}
  \frac{\partial f_{(k+1)}}{\partial \rho^*} = \frac{f_{(k+1)}-f_{(k)}}{\rho_{(k+1)}^* - \rho^*_{(k)}},
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{(1)}}{\partial \rho^*} = \frac{f(\rho^*+\Delta \rho)-f(\rho^*)}{\Delta \rho},
\end{equation}
where $\Delta \rho$ is a small quatity, we define
\begin{equation}
  \Delta \rho = \frac{\rho_{(1)}^*}{100}.
\end{equation}
  \item  Evaluating  $\rho^*_{(k+1)}$:

	By the Newton iteration equation, a new density can be updated as

\begin{equation}
 \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
\end{equation}

The iteration is convergent if
The  convergence is meassured by
\begin{equation}{\label{conv1}}
  \text{CHA} \le \text{TOL},
\end{equation}
where
\begin{equation}
\text{CHA} = \text{max} \left[
\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right].
\end{equation}
and the tolerance is taken as $\text{TOL} = 10^{-4}$.

If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv1} ) is satisfied.
\end{enumerate}
\textbf{Iteration end.}
\section{Numerical  tests }
In this section, by choosing suitable initial conditions, we will solve the Riemann problem with several different structure cases in the solution.   Numerical results by the method  in \cite{liumulti} is used to verified the correctness of the exact solution. In the following tests, the materials are taken as  aluminium and copper. The parameters for the EOS and constitutive model for aluminum and copper  are
$ (\rho_0, a_0, \Gamma_0, s, \mu)_{\text{Al}} =(8930 \text{kg}/\text{m}^3, 3940 \text{m}/\text{s},2, 1.49, 2.76 ,2.76\times 10^{10} \text{Pa} )$ and   $(\rho_0, a_0, \Gamma_0, s, \mu)_{\text{copper}} =(2785 \text{kg}/\text{m}^3, 5328 \text{m}/\text{s},2, 1.338,4.5\times 10^{10}\text{Pa})$, respectively. The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.

@@

\includegraphics[width= 8cm] {case1rho.pdf}
\includegraphics[width= 8cm] {case1u.pdf}
\includegraphics[width= 8cm] {case1p.pdf}
\includegraphics[width= 8cm] {case1sigma.pdf}

    \caption{Comparison resutls for Test 1 with the structrures of $S^P|S^P$.  }
  \label{fig:case1}
\end{figure}
\subsection{Test 2}
Next, we consider a case with yielding process at both sides, so the result has five waves. The initial condition is
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 800\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, besides the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
\begin{figure}
  \centering
  \includegraphics[width= 8cm] {case2rho.pdf}
  \includegraphics[width= 8cm] {case2u.pdf}
  \includegraphics[width= 8cm] {case2p.pdf}
  \includegraphics[width= 8cm] {case2sxx.pdf}
  \caption{Comparison resutls for Test 2 with the structrures of $S^ES^P|S^PS^E$.  }
  \label{fig:case2}
\end{figure}

@@

  \includegraphics[width= 8cm] {case4rho.pdf}
  \includegraphics[width= 8cm] {case4u.pdf}
  \includegraphics[width= 8cm] {case4p.pdf}
  \includegraphics[width= 8cm] {case4sxx.pdf}

@@

 \includegraphics[width= 8cm] {case3rho.pdf}
  \includegraphics[width= 8cm] {case3u.pdf}
  \includegraphics[width= 8cm] {case3p.pdf}
  \includegraphics[width= 8cm] {case3sxx.pdf}

    \caption{Comparison resutls for Test 4 with the structrures of $R^ER^P|R^PR^E$.  }
  \label{fig:case4}
\end{figure}
\subsection{Test 5}
In Test 4, the material is  yielding from a elastic state to a plastic state through  an elastic rarefaction wave, just as we say in the introduction, 
even when it is in the plastic state at the beginning, after a rarefaction wave, the material will return into an elastic state and then may change into the  plastic by an  expandation yielding process. This is shown in Fig.\ref{fig:case20} both by the numerical and theoretical results, the material truely change from plastic state to elastic then to plastic state again. The initial conditions are 
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -200\text{m}/\text{s}, \quad  p = 1.0 \text{Pa}, \quad  s_{xx}=-2.0\time 10^8 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}= -2.0 \time 10^8 \text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
\begin{figure}
  \centering
 \includegraphics[width= 8cm] {case20rho.pdf}
  \includegraphics[width= 8cm] {case20u.pdf}
  \includegraphics[width= 8cm] {case20p.pdf}
  \includegraphics[width= 8cm] {case20sxx.pdf}
    \caption{Comparison resutls for Test 5 with the structrures of $R^ER^P|R^PR^E$.  }
  \label{fig:case20}
\end{figure}
\subsection{Test 6}
All the above five tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
&	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 1.0\times 10^8\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -40\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
In the Fig.\ref{fig:case5} shown in both the numerical and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.

@@

  \includegraphics[width= 8cm] {case5rho.pdf}
  \includegraphics[width= 8cm] {case5u.pdf}
  \includegraphics[width= 8cm] {case5p.pdf}
  \includegraphics[width= 8cm] {case5sxx.pdf}

    \caption{Comparison resutls for Test 6 with the structrures of $R^P|R^PR^E$.  }
  \label{fig:case5}
\end{figure}
\subsection{Test 7}
In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves producted into the higher pressure side and shock waves generated into the lower pressure side. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10} \text{Pa}, \quad s_{xx}= 0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side.
\begin{figure}
  \centering

  \includegraphics[width= 8cm] {case9rho.pdf}
  \includegraphics[width= 8cm] {case9u.pdf}
  \includegraphics[width= 8cm] {case9p.pdf}
  \includegraphics[width= 8cm] {case9sxx.pdf}

    \caption{Comparison resutls for Test 7 with the structrures of $R^ER^P|S^PS^E$.  }
  \label{fig:case9}
\end{figure}
\subsection{Test 8}
Now we will consider two multi-material tests with different materials on different sides. In this test, on the left side, a lighter material of aluminum with a velocity impacts to a heavier material of copper. The initial condition is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa},\\
	 &	 \text{R: Copper,}\quad  \rho = 8930\text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p =0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Show in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface. The exact Riemann solver can solve the Riemann problem with multi-materials very well comparing to the MHLLCEP approximate solver.

\begin{figure}
  \centering
  \includegraphics[width= 8cm] {case6rho.pdf}
  \includegraphics[width= 8cm] {case6u.pdf}
  \includegraphics[width= 8cm] {case6p.pdf}
  \includegraphics[width= 8cm] {case6sigma.pdf}

    \caption{Comparison results for Test 8 with structrures of $R^ER^P|R^PR^E$.  }
  \label{fig:case7}
\end{figure}

%In this paper,  the multi-material HLLC-type  approximate Riemann solver with both the elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic  flows with a hypo-elastic model and the von Mises yielding condition. During constructing the  MHLLCEP, we do not use the assumption in which the pressure is continuous across the contact wave and so describing and evaluating the plastic waves are  more accurate than that in the  HLLCE.  Based on the MHLLCEP,
%combining with the third-order ghost-cell reconstruction method and the third-order TVD-Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic flows is built. Verified by the numerical experiments, both the plastic waves and elastic waves can be resolved correctly, our scheme appears to be convergent, stable, essentially non-oscillatory and can reach third-order accuracy for smooth problems. Especially for multi-material elastic-plastic flows, the results solved by the scheme with HLLCE are with large errors, but our new scheme can eliminate these errors and leads to the reasonable numerical results.
%
%
\subsection{Test 9}
At last, we test another multi-materials case, in this test the initial condtion is given as
\begin{equation}
 \left\{ \begin{aligned}
	 &	 \text{L: Copper,}\quad  \rho = 8930 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10}\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 10.0 \text{Pa}, \quad  s_{xx}=0.0 \text{Pa}.\\
   \end{aligned}
 \right.
\end{equation}
Shown in Fig.\ref{fig:case8}, there are two rarefaction waves on the left side and two shocks on the right side, there is a discontinuity of pressure on the interface, and the Cauchy stress is continuous, which  meets with the theoretical analysis.
\begin{figure}
  \centering
  \includegraphics[width= 8cm] {case8rho.pdf}
  \includegraphics[width= 8cm] {case8u.pdf}
  \includegraphics[width= 8cm] {case8p.pdf}
  \includegraphics[width= 8cm] {case8sigma.pdf}

    \caption{Comparison results for Test 9 with the structrures of $R^ER^P|S^ES^P$.  }
  \label{fig:case8}
\end{figure}
\subsection{Test 10}
Then we give two tests of  half Riemann problem, the first is with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
\begin{equation}
 \text{Copper,}\quad\rho = 8930\text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p =0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa}.
\end{equation}
In Fig.\ref{fig:case9}, comparason results are given by the exact half Riemann solver and the numerical method. We can see that the exact solver  can resolve both the elastic and plastic shock waves well.
\begin{figure}
  \centering
  \includegraphics[width= 8cm] {case10rho.pdf}
  \includegraphics[width= 8cm] {case10u.pdf}
  \includegraphics[width= 8cm] {case10p.pdf}
  \includegraphics[width= 8cm] {case10sxx.pdf}
